Data Management for LSST Special Programs

### 2023-10-19 sec_req.tex
minor edits

\textbf{Produce unique and special (and joinable) data products when possible --}
Rubin Observatory and the LSST system (the observatory and the data 
management systems) are required to process Special Programs data to 
produce unique and separate data products ``whenever possible" 
(LSR-REQ-0121).

@@

It is a requirement that these Special Programs data products be distinct, 
and joinable with (in other words, they can be federated or cross-matched 
with) the Prompt and Data Release data products (DMS-REQ-0322).

\textbf{The data products' size should be about 10\% of the WFD programs' --}
It is a requirement that the cumulative size of the Special Programs data 
products generated by Rubin Observatory be no more than $\sim$10\% the 
size of the Data Release data products (LSR-REQ-0121).
The spirit of this requirement is that the size be proportional to the fraction 
of survey time spent on Special Programs.

@@

\textbf{Store metadata sufficient to trigger Special Processing -- }
In order to support Special Programs processing, the LSST system is 
required to store metadata that includes program information for every raw 
image, such as identifiers for images obtained as part of the Main Survey 
or a Special Program (DMS-REQ-0068).
It is required that this metadata be sufficient for Special Programs to 
trigger their own real-time data processing recipes ``whenever possible" 
(DMS-REQ-0320), and be included in alert packets (DMS-REQ-0274).

@@

\textbf{Latency requirements apply to alerts from Special Programs images --}
It is a requirement that any Special Programs processing done with the 
Prompt pipeline (or a reconfigured version of it) is subject to the same 
timescales and latency constraints of 24 hours for the release of Prompt 
data products and 1 minute for the transmission of Alert packets 
(DMS-REQ-0344).

\textbf{Intermediate timescales should be used to enable science --}
It is also a requirement that Special Programs processing be done on 
timescales intermediate to the Prompt and Data Release processing, 
``whenever possible" and whenever necessary to enable the intended science 
goals of the Special Program (LSR-REQ-0032).

\textbf{Exposure times of 1 second must be processable -- }
It is a requirement that the LSST system be able to process non-standard 
visits with short exposure times as low as 1 second, with a discussion 
note that such short exposures might have degraded image quality 
(LSR-REQ-0111).

>>>>

\textbf{Produce unique and special (and joinable) data products when possible. --}
Rubin Observatory and the LSST system (the observatory and the data 
management systems) are required to process Special Programs data to 
produce unique and separate data products ``whenever possible" 
(LSR-REQ-0121).
It is a requirement that these Special Programs data products be distinct 
and joinable with the Prompt and/or Data Release data products (DMS-REQ-0322).

@@

The term ``joinable" means the Special Programs data products can be federated 
or cross-matched with the relevant Prompt and Data Release data products, and that
a column of cross-matched object identifiers is provided to enable table joins.

\textbf{The size of Special Programs data products should be about 10\% of the total. --}
It is a requirement that the cumulative size of the Special Programs data 
products generated by Rubin Observatory be no more than $\sim$10\% the 
size of the Data Release data products (LSR-REQ-0121).

The spirit of this requirement on data volume is that the size be proportional to the fraction 
of survey time spent on Special Programs.

@@

\textbf{Program metadata that is sufficient to trigger Special Processing should be stored. -- }
In order to support Special Programs processing, the LSST system is 
required to store metadata that includes program information for every raw 
image, such as identifiers for images obtained as part of the Main Survey 
or a Special Program (DMS-REQ-0068).
It is required that this metadata be sufficient for Special Programs to 
trigger their own real-time data processing recipes ``whenever possible" 
(DMS-REQ-0320), and be included in alert packets (DMS-REQ-0274).

@@

\textbf{Latency requirements apply to alerts from Special Programs images. --}
It is a requirement that any Special Programs processing done with the 
Prompt pipeline (or a reconfigured version of it) is subject to the same 
timescales and latency constraints of 24 hours for the release of Prompt 
data products and 1 minute for the transmission of Alert packets 
(DMS-REQ-0344).

\textbf{Intermediate timescales should be used to enable science when needed. --}
It is also a requirement that Special Programs processing be done on 
timescales intermediate to the Prompt and Data Release processing, 
``whenever possible" and whenever necessary to enable the intended science 
goals of the Special Program (LSR-REQ-0032).

\textbf{Exposure times of 1 second should be processable. -- }
It is a requirement that the LSST system be able to process non-standard 
visits with short exposure times as low as 1 second, with a discussion 
note that such short exposures might have degraded image quality 
(LSR-REQ-0111).
